---
title: "Informal Rust Gamedev in 2024 Survey"
author: "Jan Hohenheim"
date: "2024-05-04"
output: 
  pdf_document: 
    latex_engine: xelatex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Dependencies

```{r, message = F}
library(tidyverse)
library(glue)
library(ggthemes)
library(latex2exp)
library(glmnet)
library(MASS)
library(rstatix)
library(ordinal)

theme_set(theme_solarized_2())
```

## Data Cleaning

```{r}
dat_raw <- read_csv("data_original.csv")
```

```{r}
dat <- dat_raw |>
  # Change names
  ## Timestamp
  rename_at(1, ~ "timestamp") |>
  ## On a scale of 1 to 5, how high is your excitement for the newsletter in its current form?
  rename_at(2, ~ "excitement") |>
  ## How would you change the amount of content per newsletter? (e.g. have 2 library updates instead of 5)
  rename_at(3, ~ "amount") |>
  ## How would you change the frequency of the newsletter?
  rename_at(4, ~ "frequency") |>
  ## How would you feel if some minor content of the newsletter was generated by an AI if the maintainers didn't get to it in time? This content would still be checked and edited by a human before release.
  rename_at(5, ~ "ai") |>
  ## The current tone of voice in the newsletter is...
  rename_at(6, ~ "tone") |>
  ## How often have you contributed to the newsletter before?
  rename_at(7, ~ "contributions") |>
  ## On a scale of 1-5, how easy is the current process for contributing to the newsletter? Leave this out if you've never interacted with this process.
  rename_at(8, ~ "ease") |>
  ## How do you usually get informed about a new edition of the newsletter?
  rename_at(9, ~ "informed") |>
  ## What about the newsletter do you like and wish to not be changed?
  rename_at(10, ~ "like") |>
  ## What is the most important thing to improve about the newsletter?
  rename_at(11, ~ "improve") |>
  ## Is there something else you would like to tell us?
  rename_at(12, ~ "comment") |>
  # Rename factors
  mutate(
    amount = fct_recode(amount, 
      less = "less content; keep only the most important news",
      leave = "leave it as-is",
      more = "more content; add sections for minor news",
      dont_care = "I don't care",
    ),
    frequency = fct_recode(frequency,
      weekly = "make it weekly",
      monthly = "leave it monthly",
      quarterly = "make it quarterly",
      dont_care = "I don't care",
    ),
    ai = fct_recode(ai,
      not_okay = "not okay at all",
      okay = "not ideal, but okay",
      good = "sounds like a good idea",
      love = "I love this",
      dont_care = "I don't care",
    ),
    tone = fct_recode(tone,
      too_formal = "too formal",
      just_right = "just right",
      too_casual = "too informal",
    ),
    contributions = fct_recode(contributions,
      "0" = "never",
      "1" = "once",
      "2-5" = "2-5 times",
      ">5" = "more than 5 times",
    ),
    informed = fct_recode(informed,
      TODO
    )
  )
